---
title: "論文レポート"
output: html_document
theme: cerulean
---
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>

<style type="text/css">

body{ /* Normal  */
      font-size: 16px;
  }
td {  /* Table  */
  font-size: 10px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 14px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 16px;
}
</style>

## PMID & 著者
```{r, echo=F}
message(paste("PMID: ", translatedResults[[1]]))
print(translatedResults[[2]])
```

## 雑誌名
```{r, echo=F}
message(translatedResults[[3]][1], "\n", translatedResults[[3]][2])
```

## 論文名
```{r, echo=F}
message(translatedResults[[4]][1], "\n", translatedResults[[4]][2])
```
## 要旨
```{r, echo=F, fig.height=3}
message(translatedResults[[5]][1])
message(translatedResults[[5]][2])
```

